Dancing on Water: The Choreography of Sulfur Dioxide Adsorption to Aqueous Surfaces

### 2011-10-19 EquilibratedOrientation.tex
merging

In the interfacial region the angular distribution of the single \suldiox~(in the neat-water system) is concentrated primarily in $\theta \lt$ 90 \textdegree. The peak of the distribution occurs at $\theta)=$ 0\textdegree. This indicates that the \suldiox~bisector points out of the water surface, with the sulfur atom pointing towards the aqueous bulk, and the two oxygens pointing into the gas phase. This same distribution occurs in the saturated system for depths below the surface location, $\lt 0$\angs. Beyond 4\angs~above the surface, both distributions become mostly isotropic, either because the \suldiox~does not venture into the gas in the neat-water system, or because of the nature of the adsorbed \suldiox~layer in the saturated system. Promixity to the water surface highly orients the \suldiox~bisector. % with the sulfur atom pointing in towards the water bulk. %Moving further away from the water surface, and interacting less with \wat~molecules allows for greater orientational freedom as exhibited in the isotropy of the distributions above 4\angs. %Because both the neat-water and saturated systems show rather similar distributions, it is possible that the concentration of \suldiox~does not strongly affect the orientation of the \suldiox, unlike the orientations of waters.

>>>>

In the interfacial region the angular distribution of the single \suldiox~(in the neat-water system) is concentrated primarily in $\theta <$ 90 \textdegree. The peak of the distribution occurs at $\theta)=$ 0\textdegree. This indicates that the \suldiox~bisector points out of the water surface, with the sulfur atom pointing towards the aqueous bulk, and the two oxygens pointing into the gas phase. This same distribution occurs in the saturated system for depths below the surface location, $< 0$\angs. Beyond 4\angs~above the surface, both distributions become mostly isotropic, either because the \suldiox~does not venture into the gas in the neat-water system, or because of the nature of the adsorbed \suldiox~layer in the saturated system. Promixity to the water surface highly orients the \suldiox~bisector. % with the sulfur atom pointing in towards the water bulk. %Moving further away from the water surface, and interacting less with \wat~molecules allows for greater orientational freedom as exhibited in the isotropy of the distributions above 4\angs. %Because both the neat-water and saturated systems show rather similar distributions, it is possible that the concentration of \suldiox~does not strongly affect the orientation of the \suldiox, unlike the orientations of waters.
